\propertitle

### 2019-06-12 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-12T11:01:28+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In the present work we give an answer to this question: What inferences
about the \emph{total activity} of a large neuronal network can we make by
recording a very small sample thereof? We'll first give an answer by
combining, in a straightforward way, the maximum-entropy method and basic
sampling relations of the probability calculus. Later on we'll show that
this answer can be obtained by exclusively using the probability calculus;
this point of view shows that the maximum-entropy answer is a first
approximation to the answers of \emph{three} different questions, and also
shows the assumptions lying behind it.

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-12T16:15:50+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In the present work we give an answer to this question: What inferences
about the \emph{total activity} of a large neuronal network can we make by
recording a very small sample thereof? We'll first give an answer by
combining, in a straightforward way, the maximum-entropy method and basic
sampling relations of the probability calculus. Later on we'll show that
this answer can be obtained by exclusively using the probability calculus;
this point of view shows that the maximum-entropy answer is a first
approximation to the answers of \emph{four} different questions, and also
shows the assumptions lying behind it.

@@

\section{Model: maximum-entropy and sampling}
\label{sec:model}

The idea behind the approach is easily summarized:
\begin{enumerate*}[label=(\alph*)]
  \item\label{item:maxent_step} we build a distribution for the total
  activity of the full population using the maximum-entropy method;
  \item\label{item:sample_step} the expectation constraints used in the
  method for the full population are, in turn, determined via sampling
  theory from the expectation constraints for the sample.
\end{enumerate*}

Regarding point~\ref{item:maxent_step}, we assume the reader to be familiar
with the maximum-entropy method. We add two remarks.
First, the distribution given by the method is the zeroth-order
approximation of \emph{four} distinct distributions:
\begin{itemize}
\item the probability distribution for the value of the activity at any
  time bin among those recorded,
\item the probability distribution for the value of the activity at a \emph{new}
  time bin,
\item the most probable time-frequency distribution of the activity during the
  recording,
\item the most probable time-frequency distribution of the activity in a very
  long run of new time bins.
\end{itemize}
So the generic term \enquote{distribution} means one of these four; note
that although these distributions numerically coincide in this basic
approximation, they numerically differ in higher-order approximations.
Second, the maximum-entropy method based on the Shannon entropy implicitly
makes specific assumptions about the probability of the long-run frequency
distributions \citep{jaynes1986d_r1996,portamana2009,portamana2017}.

In our case, to apply the method to the total activity of the full
population we need to set some of its expectation values, for some of its
moments for example. Here enters point~\ref{item:sample_step}:
